---
title: "Task 1 & Task 2"
author: "Yujia Wang"
date: "12/8/2021"
output:
  pdf_document: 
          latex_engine: xelatex
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=F,message = F,echo=F,highlight=F)
knitr::opts_chunk$set(fig.width=6, fig.height=4,fig.align = "center") 
```


## Task 1: Pick a book

Alice's Adventures in Wonderland is a science fiction novel that I loved to read when I was young. So I chose this book to commemorate my lost childhood.

```{r}
# input the book
library(gutenbergr)
alice0 <- gutenberg_download(gutenberg_id = 11)

# clear up the book
library(dplyr)
library(stringr)
alice1 <- alice0 %>%
          select(-gutenberg_id) %>%
          mutate(linenumber = row_number(),
          chapter = cumsum(str_detect(text, 
                                      regex("^chapter [\\divxlc]",
                                      ignore_case = TRUE)))) %>%
          filter(linenumber >= 30) %>%
          ungroup()

# prepare for the text
library(tidytext)
data(stop_words)
alice2 <- alice1 %>%
          unnest_tokens(word, text) 

#change ’ to ', otherwise stopwords can't recognize it
alice2$word <- gsub("’","'",alice2$word)

# delete the stopwords
alice2 <- alice2 %>%
          anti_join(stop_words)

# check the final data
check <- alice2 %>%
                count(word, sort = TRUE)
```

```{r, fig.cap="xxx"}
# visualization 1: the most common words
library(ggplot2)
alice2 %>%
       count(word, sort = TRUE) %>%
       filter(n > 50) %>%
       mutate(word = reorder(word, n)) %>%
       ggplot(aes(n, word)) +
       geom_col() +
       labs(y = NULL)
```

I calculated the eight most frequent words in the book, and the results are as follows. It can be found that because Alice is the protagonist, the frequency of using her name is much higher than other words.

At the same time, there are 5 words that are the names of characters, such as Queen, King, Turtle, Hatter and Gryphon, which shows that they are the main supporting roles of the book.

Time is the second most frequent word in this book, reflecting the urgency of Alice's adventure in her dream.


## TASK 2: bag of word analysis

```{r}
# input lexicons
library(tidytext)
get_sentiments("afinn")
get_sentiments("bing")
get_sentiments("nrc")

# fliter nrc: joy
nrc_joy <- get_sentiments("nrc") %>% 
  filter(sentiment == "joy")

alice2 %>%
       inner_join(nrc_joy) %>%
       count(word, sort = TRUE)

# bing: positive - negative
library(tidyr)
alice_sentiment <- alice2 %>%
  inner_join(get_sentiments("bing")) %>%
  count(index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(sentiment = positive - negative)
```

Based on the plot trajectory of Alice's Adventures in Wonderland, I calculated the emotional score. The x-axis tracks the narrative time in the text part, and the y-axis is the difference between positive and negative emotions.

```{r, fig.cap="xxx"}
# visualization 2: sentiment scores across the plot trajectory
ggplot(alice_sentiment, aes(index, sentiment)) +
  geom_col(show.legend = FALSE)
```

It can be seen that almost all the plots in this book are negative emotions. This result coincides with the book's absurd, bizarre fictional scenes, weird characters, and thrilling adventure stories.

```{r}
# prepare for comparing the three sentiment dictionaries
afinn <- alice2 %>% 
         inner_join(get_sentiments("afinn")) %>% 
         group_by(index = linenumber %/% 80) %>% 
         summarise(sentiment = sum(value)) %>% 
         mutate(method = "AFINN")

bing_and_nrc <- bind_rows(
                alice2 %>% 
                       inner_join(get_sentiments("bing")) %>%
                        mutate(method = "Bing et al."),
                alice2 %>% 
                       inner_join(get_sentiments("nrc") %>% 
                       filter(sentiment %in% c("positive", "negative"))) %>%
                       mutate(method = "NRC")) %>%
                count(method, index = linenumber %/% 80, sentiment) %>%
                pivot_wider(names_from = sentiment,
                            values_from = n,
                            values_fill = 0) %>% 
                mutate(sentiment = positive - negative)
```

### comparing the three sentiment dictionaries

```{r, fig.cap="xxx"}
# visualization 3: comparing the three sentiment dictionaries
bind_rows(afinn, bing_and_nrc) %>%
                               ggplot(aes(index, sentiment, fill = method)) +
                               geom_col(show.legend = FALSE) +
                               facet_wrap(~method, ncol = 1, scales = "free_y")
```

According to text mining with R, I imported AFINN dictionary, Bing dictionary and NRC dictionary. It can be seen that the results of AFINN and Bing tend to be consistent, but the results of NRC are more positive, and the result of AFINN has more variance.

```{r}
# count the most common positive and negative words
bing_word_counts <- alice2 %>%
                           inner_join(get_sentiments("bing")) %>%
                           count(word, sentiment, sort = TRUE) %>%
                           ungroup()
```

```{r, fig.cap="xxx"}
# visualization 4: the most common positive and negative words
bing_word_counts %>%
                 group_by(sentiment) %>%
                 slice_max(n, n = 10) %>% 
                 ungroup() %>%
                 mutate(word = reorder(word, n)) %>%
                 ggplot(aes(n, word, fill = sentiment)) +
                 geom_col(show.legend = FALSE) +
                 facet_wrap(~sentiment, scales = "free_y") +
                 labs(x = "Contribution to sentiment", y = NULL)
```

\newpage

### word cloud

The plot above shows the 12 most frequently positive or negative words.

```{r fig.width=6, fig.height=4,fig.cap="sentiment word cloud"}
# visualization 5: wordclouds 1
library(wordcloud)
alice2 %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 55,random.order=TRUE, colors=c("palegreen3","lightpink1")))
```

```{r fig.width=6, fig.height=4,fig.cap="sentiment word cloud"}
# visualization 6: wordclouds 2
library(reshape2)
alice2 %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("brown2", "skyblue2"),
                   max.words = 50)
```

Subsequently, I drew two word cloud plots of frequency. This is the visualization of the previous plot.

\newpage

## Extra credit: another lexicon

Coincidentally, I found a new method when the system reported an error, which said "Error in match.arg(lexicon) : 'arg' should be one of “bing”, “afinn”, “loughran”, “nrc”".

```{r}
# another method
alice_loughran <- alice2 %>%
  inner_join(get_sentiments("loughran")) %>%
  count(index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(sentiment = positive - negative) %>%
  mutate(method = "LOUGHRAN")
```

```{r, fig.cap="xxx"}
# visualization 7: 
ggplot(alice_loughran, aes(index, sentiment)) +
  geom_col(show.legend = FALSE)
```

### comparing the four sentiment dictionaries

Finally, I drew a comparison chart of the four methods. I found that loughran is like a neutralized version of AFINN and Bing. Maybe this is a more reliable sentiment analysis package.

```{r, fig.cap="xxx"}
# visualization 8: comparing the three sentiment dictionaries
bind_rows(afinn, bing_and_nrc, alice_loughran) %>%
                               ggplot(aes(index, sentiment, fill = method)) +
                               geom_col(show.legend = FALSE) +
                               facet_wrap(~method, ncol = 1, scales = "free_y")
```

\newpage

## Reference 

[https://www.gutenberg.org/ebooks/11](https://www.gutenberg.org/ebooks/11)
[https://www.tidytextmining.com/sentiment.html](https://www.tidytextmining.com/sentiment.html)
[https://www.rdocumentation.org/packages/textdata/versions/0.4.1](https://emilhvitfeldt.github.io/textdata/reference/lexicon_loughran.html)
[https://www.rdocumentation.org/packages/textdata/versions/0.4.1/topics/lexicon_loughran](https://www.rdocumentation.org/packages/textdata/versions/0.4.1/topics/lexicon_loughran)


