---
title: "Task 1 & Task 2"
author: "Yujia Wang"
date: "12/8/2021"
output:
  pdf_document: 
          latex_engine: xelatex
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=F, message = F, echo=F, highlight=F)
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.align = "center") 
```


## Task 1: Pick a book

Alice's Adventures in Wonderland is a children literature that I loved to read when I was young. So I chose this book to look back at my childhood.

```{r}
# input the book
library(gutenbergr)
alice0 <- gutenberg_download(gutenberg_id = 11)

# clear up the book
library(dplyr)
library(stringr)
alice1 <- alice0 %>%
          select(-gutenberg_id) %>%
          mutate(linenumber = row_number(),
          chapter = cumsum(str_detect(text, 
                                      regex("^chapter [\\divxlc]",
                                      ignore_case = TRUE)))) %>%
          filter(linenumber >= 30) %>%
          ungroup()

# prepare for the text
library(tidytext)
data(stop_words)
alice2 <- alice1 %>%
          unnest_tokens(word, text) 

#change ’ to ', otherwise stopwords can't recognize it
alice2$word <- gsub("’","'",alice2$word)

# delete the stopwords
alice2 <- alice2 %>%
          anti_join(stop_words)

# check the final data
check <- alice2 %>%
                count(word, sort = TRUE)
```

```{r, fig.cap="the eight most common words"}
# visualization 1: the eight most common words
library(ggplot2)
alice2 %>%
       count(word, sort = TRUE) %>%
       filter(n > 50) %>%
       mutate(word = reorder(word, n)) %>%
       ggplot(aes(n, word)) +
       geom_col() +
       labs(y = NULL)
```

I calculated the eight most frequent words in the book, and the results are as follows. It can be found that because Alice is the protagonist, the frequency of using her name is much higher than other words.

At the same time, there are 5 words that are the names of characters, such as Queen, King, Turtle, Hatter and Gryphon, which shows that they are the main supporting roles of the book.

Time is the second most frequent word in this book, reflecting Alice raced against time in her adventure.


## Task 2: bag of word analysis

```{r, results='hide'}
# input lexicons
library(tidytext)
#get_sentiments("afinn")
#get_sentiments("bing")
#get_sentiments("nrc")

# fliter nrc: joy
nrc_joy <- get_sentiments("nrc") %>% 
           filter(sentiment == "joy")

alice2 %>%
       inner_join(nrc_joy) %>%
       count(word, sort = TRUE)

# bing: positive - negative
library(tidyr)
alice_sentiment <- alice2 %>%
  inner_join(get_sentiments("bing")) %>%
  count(index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(sentiment = positive - negative)
```

```{r, fig.cap="sentiment scores"}
# visualization 2: sentiment scores across the plot trajectory
ggplot(alice_sentiment, aes(index, sentiment)) +
  geom_col(show.legend = FALSE)
```

Based on the plot trajectory of Alice's Adventures in Wonderland, I calculated the emotional score. The x-axis tracks the narrative time in the text part, and the y-axis is the difference between positive and negative emotions. It can be seen that almost all the plots in this book are negative emotions. 

This book is about Alice falling into a rabbit hole by accident. She met a lot of strange people and animals, such as the playing cards behind a small door, the rough queen of hearts. In this world of fantasy and madness, Alice fights against violence and helps others. 

So figure 2 coincides with the book's absurd, bizarre fictional scenes, weird characters, and thrilling adventure stories.


\newpage


### Comparing the three sentiment dictionaries

```{r}
# prepare for comparing the three sentiment dictionaries
afinn <- alice2 %>% 
         inner_join(get_sentiments("afinn")) %>% 
         group_by(index = linenumber %/% 80) %>% 
         summarise(sentiment = sum(value)) %>% 
         mutate(method = "AFINN")

bing_and_nrc <- bind_rows(
                alice2 %>% 
                       inner_join(get_sentiments("bing")) %>%
                        mutate(method = "Bing et al."),
                alice2 %>% 
                       inner_join(get_sentiments("nrc") %>% 
                       filter(sentiment %in% c("positive", "negative"))) %>%
                       mutate(method = "NRC")) %>%
                count(method, index = linenumber %/% 80, sentiment) %>%
                pivot_wider(names_from = sentiment,
                            values_from = n,
                            values_fill = 0) %>% 
                mutate(sentiment = positive - negative)
```

```{r, fig.cap="comparing the three sentiment dictionaries"}
# visualization 3: comparing the three sentiment dictionaries
bind_rows(afinn, bing_and_nrc) %>%
                               ggplot(aes(index, sentiment, fill = method)) +
                               geom_col(show.legend = FALSE) +
                               facet_wrap(~method, ncol = 1, scales = "free_y")
```

According to text mining with R, I imported AFINN dictionary, Bing dictionary and NRC dictionary. It can be seen that the results of AFINN and Bing tend to be consistent, but the results of NRC are more positive, and the result of AFINN has more variance.


\newpage


### The most common positive and negative words

```{r}
# count the most common positive and negative words
bing_word_counts <- alice2 %>%
                           inner_join(get_sentiments("bing")) %>%
                           count(word, sentiment, sort = TRUE) %>%
                           ungroup()
```

```{r, fig.cap="the most common positive and negative words"}
# visualization 4: the most common positive and negative words
bing_word_counts %>%
                 group_by(sentiment) %>%
                 slice_max(n, n = 10) %>% 
                 ungroup() %>%
                 mutate(word = reorder(word, n)) %>%
                 ggplot(aes(n, word, fill = sentiment)) +
                 geom_col(show.legend = FALSE) +
                 facet_wrap(~sentiment, scales = "free_y") +
                 labs(x = "Contribution to sentiment", y = NULL)
```

Figure 4 shows the 12 most frequently positive and negative words. We can see that negative words are more than positive words in the book. Among them, mock is usually used to describe the action state of the characters, and express the absurd content of the story. And beautiful is more used to express the environment, reflecting that Alice has entered a fantasy and extraordinary world of fiction. 


### Word cloud

```{r fig.width=4, fig.height=4,fig.cap="sentiment word cloud version 1"}
# visualization 5: wordclouds 1
library(wordcloud)
alice2 %>%
  anti_join(stop_words) %>%
  count(word) %>%
  with(wordcloud(word, n, max.words = 55,random.order=TRUE, colors=c("palegreen3","lightpink1")))
```

```{r fig.width=6, fig.height=4,fig.cap="sentiment word cloud version 2"}
# visualization 6: wordclouds 2
library(reshape2)
alice2 %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0) %>%
  comparison.cloud(colors = c("brown2", "skyblue2"),
                   max.words = 50)
```

Subsequently, I drew two word cloud plots of words frequency. These are the visualization of the previous plot.


\newpage


## Extra credit: another lexicon

Coincidentally, I found a new method "loughran" when the system reported an error, which said "Error in match.arg(lexicon) : 'arg' should be one of “bing”, “afinn”, “loughran”, “nrc”".

```{r}
# another method
alice_loughran <- alice2 %>%
  inner_join(get_sentiments("loughran")) %>%
  count(index = linenumber %/% 80, sentiment) %>%
  pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
  mutate(sentiment = positive - negative) %>%
  mutate(method = "LOUGHRAN")
```

```{r, fig.cap="sentiment scores using loughran"}
# visualization 7: 
ggplot(alice_loughran, aes(index, sentiment)) +
  geom_col(show.legend = FALSE)
```

Figure 7 shows the sentiment score along the story line  using loughran dictionary. The results are almost all negative emotions, consistent with the results of other dictionaries. 


\newpage


### Comparing the four sentiment dictionaries

```{r, fig.cap="comparing the four sentiment dictionaries"}
# visualization 8: comparing the four sentiment dictionaries
bind_rows(afinn, bing_and_nrc, alice_loughran) %>%
                               ggplot(aes(index, sentiment, fill = method)) +
                               geom_col(show.legend = FALSE) +
                               facet_wrap(~method, ncol = 1, scales = "free_y")
```

Finally, I drew a comparison chart of the four methods. I found that loughran is like a neutralized version of AFINN and Bing. Maybe this is a more reliable sentiment analysis package.


## Reference 

Gutenberg. (2008). Alice's Adventures in Wonderland by Lewis Carroll [online]. Available from: https://www.gutenberg.org/ebooks/11 [accessed 8 December 2021]

Julia Silge and David Robinson. (unknow time). Text Mining with R: A Tidy Approach [online]. Available from: https://www.tidytextmining.com/sentiment.html [accessed 8 December 2021]

Rdocumentation. (unknow time). textdata [online]. Available from: https://www.rdocumentation.org/packages/textdata/versions/0.4.1 [accessed 8 December 2021]

Rdocumentation. (unknow time). lexicon_loughran: Loughran-McDonald sentiment lexicon [online]. Available from: https://www.rdocumentation.org/packages/textdata/versions/0.4.1/topics/lexicon_loughran [accessed 8 December 2021]


